---
title: 'WFP-CNC EFSA22: Recogida de Datos - 01/08/2022 11:00'
output:
always_allow_html: true
html_document: default
---

<style type="text/css">
.main-container {
  max-width: 1800px;
  margin-left: auto;
  margin-right: auto;
}


</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = FALSE,comment = NA, message = FALSE, warning=FALSE, fig.align = 'center' )
```
```{r, include=FALSE}
library(dplyr)
library(lubridate)
library(readxl)
library(kableExtra)
library(knitr)
library(readr)
library(htmltools)
library(openxlsx)
library(janitor)
library(sf)
library(DT)
library(raster)
library(Hmisc)
library(rsconnect)
library(leaflet)
library(htmlwidgets)
library(stringr)
library(stringi)
```
```{r, include=FALSE}

options(dplyr.summarise.inform = FALSE)

WGS84 <- raster::crs("+init=epsg:4326")
UTM38N <- raster::crs("+init=epsg:32638")

assessment_start_date <- as.Date("2022-08-01")

##### set min time and max # interviews per day

delete_time_limit <- 20
flag_time_limit <- 35


dat <- read.csv("Input/efsa_all_data_2022-08-01.csv",
               stringsAsFactors = TRUE)

n_dat <- read.csv("Input/nutritional_data/nutritional_data_2022-08-01.csv",
               stringsAsFactors = TRUE)

########## LOAD SHAPE FILES ########################
adm <- st_read("Input/shapefiles_unzipped/col_admbnda_adm1_mgn_20200416.shp") %>% 
  st_transform(crs = 4326)


# change accented letters in department names
accented_letters <- function (x){
  stri_replace_all_fixed(x,
                         c("á","é","ń","í","ó","ú","ñ","ü","Á","Ó","Í","Ñ"),
                         c("a","e","n","i","o","u","n","u","A","O","I","N"),
                         vectorize_all = FALSE)
}

adm$ADM1_ES <- accented_letters(adm$ADM1_ES)

#############################
# set string to lower case and replace everything that is not alphanumeric or underscore by a dot "."
to_alphanumeric_lowercase <- function (x)
{
  tolower(gsub("[^a-zA-Z0-9_]", "\\_", x))
}

adm$ADM1_ES <- to_alphanumeric_lowercase(adm$ADM1_ES)
adm$ADM1_ES
names(adm)[names(adm) == "ADM1_ES"] <- "departamento"
adm$departamento[adm$departamento == "bogota__d_c_"] <- "bogota_dc"



########## SAMPLE FRAMES ########################
library(readxl)
strata_region <- read.csv("Input/sample_col_efsa22.csv", sep = ";")


permanencia_sample_df_summarized <- strata_region %>% 
  dplyr::filter(pop_group == "vocacion_permanencia")


retornados_sample_df_summarized <- strata_region %>% 
  dplyr::filter(pop_group == "retornados")


pendularios_sample_df_summarized <- strata_region %>% 
  dplyr::filter(pop_group == "pendularios")


acogida_sample_df_summarized <- strata_region %>% 
  dplyr::filter(pop_group == "comunidad_acogida")


transito_sample_df_summarized <- strata_region %>% 
  dplyr::filter(pop_group == "migrantes_transito")

```
```{r, include=FALSE}
########################################################################################

### Interview method 
interview_method <- dat %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento,
                Grupo_Poblacion = pop_group) %>% 
  group_by(Departamento, Grupo_Poblacion) %>% tally(name = "Number_of_interviews")
interview_method


interview_method_date <- dat %>% 
  dplyr::filter(date_assessment >= assessment_start_date) %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento) %>% 
  group_by(Fecha) %>% tally(name = "Number_of_interviews")
interview_method_date

# library(plotly)
# survey_method_graph <- plot_ly(interview_method_date, x = ~Date, y = ~Number_of_interviews, name = 'Number of Interviews Per Day', type = 'scatter', mode = 'lines',
#         line = list(color = 'rgb(205, 12, 24)', width = 4))
# survey_method_graph
# interview_method Wide format
interview_method_wide <- tidyr::pivot_wider(interview_method, 
                                            names_from = Grupo_Poblacion, 
                                            values_from = Number_of_interviews,
                                            values_fill = list(Number_of_interviews = 0))

func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
sumrow_completed <- as.data.frame(lapply(interview_method_wide, func))
sumrow_completed
interview_method_wide <- rbind(interview_method_wide, sumrow_completed ) %>% 
  mutate_all(~replace(., is.na(.), 0))



#interview_method_wide <- interview_method_wide %>% 
#  mutate(Departamento = case_when(Departamento == "west_bank" ~ "West Bank",
#                              Departamento == "gaza" ~ "Gaza",
#                              Departamento == "ej" ~ "East Jerusalem",
#                              TRUE ~ "West Bank"))

#interview_method_wide <- interview_method_wide %>% 
#  dplyr::group_by(Departamento) %>% 
#  dplyr::summarise("Number of interviews" = sum(Number_of_interviews))


```
```{r, include=FALSE}
###
### Interviews Comunidad de Acogida 

interview_method_acogida <- dat %>%
  dplyr::filter(pop_group == "comunidad_de_acogida") %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento,
                population_group = pop_group
  ) %>% 
  group_by(Departamento, population_group) %>% tally(name = "Number_of_interviews")

interview_method_acogida

interview_method_date_acogida <- dat %>% 
  dplyr::filter(date_assessment >= assessment_start_date & pop_group == "comunidad_de_acogida") %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento,
                population_group = pop_group) %>% 
  group_by(population_group, Fecha) %>% tally(name = "Number_of_interviews")

interview_method_date_acogida

# library(plotly)
# survey_method_graph_wb <- plot_ly(interview_method_date_wb, x = ~Date, y = ~Number_of_interviews, name = 'Number of Interviews West Bank', type = 'scatter', mode = 'lines',
#         line = list(color = 'rgb(205, 12, 24)', width = 4)) 
# survey_method_graph_wb
# interview_method Wide format

interview_method_wide_acogida <- tidyr::pivot_wider(interview_method_acogida, 
                                               names_from = population_group, 
                                               values_from = Number_of_interviews,
                                               values_fill = list(Number_of_interviews = 0))

interview_method_wide_acogida



### Interview method Migrantes con Vocacion de Permanencia
interview_method_permanencia <- dat %>%
  dplyr::filter(pop_group == "vocacion_de_permanencia") %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento,
                population_group = pop_group
  ) %>% 
  group_by(Departamento, population_group) %>% tally(name = "Number_of_interviews")

interview_method_permanencia

interview_method_date_permanencia <- dat %>% 
  dplyr::filter(date_assessment >= assessment_start_date & pop_group == "vocacion_de_permanencia") %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento,
                population_group = pop_group) %>% 
  group_by(population_group, Fecha) %>% tally(name = "Number_of_interviews")

interview_method_date_permanencia

# library(plotly)
# survey_method_graph_wb <- plot_ly(interview_method_date_wb, x = ~Date, y = ~Number_of_interviews, name = 'Number of Interviews West Bank', type = 'scatter', mode = 'lines',
#         line = list(color = 'rgb(205, 12, 24)', width = 4)) 
# survey_method_graph_wb
# interview_method Wide format

interview_method_wide_permanencia <- tidyr::pivot_wider(interview_method_permanencia, 
                                                    names_from = population_group, 
                                                    values_from = Number_of_interviews,
                                                    values_fill = list(Number_of_interviews = 0))

interview_method_wide_permanencia




### Interview method Retornado
interview_method_retornado <- dat %>%
  dplyr::filter(pop_group == "retornado") %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento,
                population_group = pop_group
  ) %>% 
  group_by(Departamento, population_group) %>% tally(name = "Number_of_interviews")

interview_method_retornado

interview_method_date_retornado <- dat %>% 
  dplyr::filter(date_assessment >= assessment_start_date & pop_group == "retornado") %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento,
                population_group = pop_group) %>% 
  group_by(population_group, Fecha) %>% tally(name = "Number_of_interviews")

interview_method_date_retornado

# library(plotly)
# survey_method_graph_wb <- plot_ly(interview_method_date_wb, x = ~Date, y = ~Number_of_interviews, name = 'Number of Interviews West Bank', type = 'scatter', mode = 'lines',
#         line = list(color = 'rgb(205, 12, 24)', width = 4)) 
# survey_method_graph_wb
# interview_method Wide format

interview_method_wide_retornado <- tidyr::pivot_wider(interview_method_retornado, 
                                                        names_from = population_group, 
                                                        values_from = Number_of_interviews,
                                                        values_fill = list(Number_of_interviews = 0))

interview_method_wide_retornado




### Interview method Pendularios
interview_method_pendulario <- dat %>%
  dplyr::filter(pop_group == "pendular") %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento,
                population_group = pop_group
  ) %>% 
  group_by(Departamento, population_group) %>% tally(name = "Number_of_interviews")

interview_method_pendulario

interview_method_date_pendulario <- dat %>% 
  dplyr::filter(date_assessment >= assessment_start_date & pop_group == "pendular") %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento,
                population_group = pop_group) %>% 
  group_by(population_group, Fecha) %>% tally(name = "Number_of_interviews")

interview_method_date_pendulario

# library(plotly)
# survey_method_graph_wb <- plot_ly(interview_method_date_wb, x = ~Date, y = ~Number_of_interviews, name = 'Number of Interviews West Bank', type = 'scatter', mode = 'lines',
#         line = list(color = 'rgb(205, 12, 24)', width = 4)) 
# survey_method_graph_wb
# interview_method Wide format

interview_method_wide_pendulario <- tidyr::pivot_wider(interview_method_pendulario, 
                                                        names_from = population_group, 
                                                        values_from = Number_of_interviews,
                                                        values_fill = list(Number_of_interviews = 0))

interview_method_wide_pendulario




### Interview method Migrantes en transito
interview_method_transito <- dat %>%
  dplyr::filter(pop_group == "transito") %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento,
                population_group = pop_group
  ) %>% 
  group_by(Departamento, population_group) %>% tally(name = "Number_of_interviews")

interview_method_transito

interview_method_date_transito <- dat %>% 
  dplyr::filter(date_assessment >= assessment_start_date & pop_group == "transito") %>% 
  dplyr::select(Fecha = date_assessment,
                Entrevistador = entrevistador,
                Departamento = departamento,
                population_group = pop_group) %>% 
  group_by(population_group, Fecha) %>% tally(name = "Number_of_interviews")

interview_method_date_transito

# library(plotly)
# survey_method_graph_wb <- plot_ly(interview_method_date_wb, x = ~Date, y = ~Number_of_interviews, name = 'Number of Interviews West Bank', type = 'scatter', mode = 'lines',
#         line = list(color = 'rgb(205, 12, 24)', width = 4)) 
# survey_method_graph_wb
# interview_method Wide format

interview_method_wide_transito <- tidyr::pivot_wider(interview_method_transito, 
                                                        names_from = population_group, 
                                                        values_from = Number_of_interviews,
                                                        values_fill = list(Number_of_interviews = 0))

interview_method_wide_transito




```
```{r, include=FALSE}
## Tracking by Population Group: Comunidad de Acogida
acogida_sample <- acogida_sample_df_summarized %>% 
  dplyr::select(departamento, Tamano_Muestra = sample_size)
acogida_sample


acogida_tracking <- dat %>% 
  dplyr::filter(pop_group == "comunidad_de_acogida") %>% 
  dplyr::group_by(departamento) %>% 
  dplyr::summarise(Cargado = n(),
                   Marcada_Tiempo = sum(time_validity == "Flagged", na.rm = T),
                   Borrado = sum(delete == "yes", na.rm = T),
                   Aceptado = sum(delete == "no", na.rm = T)
  )
acogida_tracking


acogida_tracking_merged <- left_join(acogida_sample, acogida_tracking, by = "departamento") %>% 
  mutate(
    Restante =  case_when(
      is.na(Aceptado) ~ Tamano_Muestra,
      TRUE ~ as.integer((Aceptado - Tamano_Muestra) * -1)))
func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
sumrow_acogida <- as.data.frame(lapply(acogida_tracking_merged, func))
sumrow_acogida
acogida_tracking_merged <- rbind(acogida_tracking_merged, sumrow_acogida ) %>% 
  mutate_all(~replace(., is.na(.), 0))
# mutate_all(funs(replace_na(.,0))) #%>% 
#   dplyr::mutate(Min_Surveys = round(Sample_Size*0.85,0)#,
#                   #Min_Remaining =  case_when(is.na(Aceptado) ~ Min_Surveys,TRUE ~ (Aceptado - Min_Surveys) * -1)
#                 )


########################################################################################
```
```{r, include=FALSE}
########################################################################################

## Tracking by Population Group: Migrantes con Vocacion de Permanencia

permanencia_sample <- permanencia_sample_df_summarized %>% 
  dplyr::select(departamento, Tamano_Muestra = sample_size)
permanencia_sample


permanencia_tracking <- dat %>% 
  dplyr::filter(pop_group == "vocacion_de_permanencia") %>% 
  dplyr::group_by(departamento) %>% 
  dplyr::summarise(Cargado = n(),
                   Marcada_Tiempo = sum(time_validity == "Flagged", na.rm = T),
                   Borrado = sum(delete == "yes", na.rm = T),
                   Aceptado = sum(delete == "no", na.rm = T)
  )
permanencia_tracking


permanencia_tracking_merged <- left_join(permanencia_sample, permanencia_tracking, by = "departamento") %>% 
  mutate(
    Restante =  case_when(
      is.na(Aceptado) ~ Tamano_Muestra,
      TRUE ~ as.integer((Aceptado - Tamano_Muestra) * -1)))
func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
sumrow_permanencia <- as.data.frame(lapply(permanencia_tracking_merged, func))
sumrow_permanencia
permanencia_tracking_merged <- rbind(permanencia_tracking_merged, sumrow_permanencia ) %>% 
  mutate_all(~replace(., is.na(.), 0))
# mutate_all(funs(replace_na(.,0))) #%>% 
#   dplyr::mutate(Min_Surveys = round(Sample_Size*0.85,0)#,
#                   #Min_Remaining =  case_when(is.na(Aceptado) ~ Min_Surveys,TRUE ~ (Aceptado - Min_Surveys) * -1)
#                 )





## Tracking by Population Group: Retornados

retornados_sample <- retornados_sample_df_summarized %>% 
  dplyr::select(departamento, Tamano_Muestra = sample_size)
retornados_sample


retornados_tracking <- dat %>% 
  dplyr::filter(pop_group == "retornado") %>% 
  dplyr::group_by(departamento) %>% 
  dplyr::summarise(Cargado = n(),
                   Marcada_Tiempo = sum(time_validity == "Flagged", na.rm = T),
                   Borrado = sum(delete == "yes", na.rm = T),
                   Aceptado = sum(delete == "no", na.rm = T)
  )
retornados_tracking


retornados_tracking_merged <- left_join(retornados_sample, retornados_tracking, by = "departamento") %>% 
  mutate(
    Restante =  case_when(
      is.na(Aceptado) ~ Tamano_Muestra,
      TRUE ~ as.integer((Aceptado - Tamano_Muestra) * -1)))
func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
sumrow_retornados <- as.data.frame(lapply(retornados_tracking_merged, func))
sumrow_retornados
retornados_tracking_merged <- rbind(retornados_tracking_merged, sumrow_retornados ) %>% 
  mutate_all(~replace(., is.na(.), 0))
# mutate_all(funs(replace_na(.,0))) #%>% 
#   dplyr::mutate(Min_Surveys = round(Sample_Size*0.85,0)#,
#                   #Min_Remaining =  case_when(is.na(Aceptado) ~ Min_Surveys,TRUE ~ (Aceptado - Min_Surveys) * -1)
#                 )



## Tracking by Population Group: Pendularios

pendularios_sample <- pendularios_sample_df_summarized %>% 
  dplyr::select(departamento, Tamano_Muestra = sample_size)
pendularios_sample


pendularios_tracking <- dat %>% 
  dplyr::filter(pop_group == "pendular") %>% 
  dplyr::group_by(departamento) %>% 
  dplyr::summarise(Cargado = n(),
                   Marcada_Tiempo = sum(time_validity == "Flagged", na.rm = T),
                   Borrado = sum(delete == "yes", na.rm = T),
                   Aceptado = sum(delete == "no", na.rm = T)
  )
pendularios_tracking


pendularios_tracking_merged <- left_join(pendularios_sample, pendularios_tracking, by = "departamento") %>% 
  mutate(
    Restante =  case_when(
      is.na(Aceptado) ~ Tamano_Muestra,
      TRUE ~ as.integer((Aceptado - Tamano_Muestra) * -1)))
func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
sumrow_pendularios <- as.data.frame(lapply(pendularios_tracking_merged, func))
sumrow_pendularios
pendularios_tracking_merged <- rbind(pendularios_tracking_merged, sumrow_pendularios ) %>% 
  mutate_all(~replace(., is.na(.), 0))
# mutate_all(funs(replace_na(.,0))) #%>% 
#   dplyr::mutate(Min_Surveys = round(Sample_Size*0.85,0)#,
#                   #Min_Remaining =  case_when(is.na(Aceptado) ~ Min_Surveys,TRUE ~ (Aceptado - Min_Surveys) * -1)
#                 )



## Tracking by Population Group: Migrantes en Transito

transito_sample <- transito_sample_df_summarized %>% 
  dplyr::select(departamento, Tamano_Muestra = sample_size)
pendularios_sample


transito_tracking <- dat %>% 
  dplyr::filter(pop_group == "transito") %>% 
  dplyr::group_by(departamento) %>% 
  dplyr::summarise(Cargado = n(),
                   Marcada_Tiempo = sum(time_validity == "Flagged", na.rm = T),
                   Borrado = sum(delete == "yes", na.rm = T),
                   Aceptado = sum(delete == "no", na.rm = T)
  )
transito_tracking


transito_tracking_merged <- left_join(transito_sample, transito_tracking, by = "departamento") %>% 
  mutate(
    Restante =  case_when(
      is.na(Aceptado) ~ Tamano_Muestra,
      TRUE ~ as.integer((Aceptado - Tamano_Muestra) * -1)))
func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
sumrow_transito <- as.data.frame(lapply(transito_tracking_merged, func))
sumrow_transito
transito_tracking_merged <- rbind(transito_tracking_merged, sumrow_transito ) %>% 
  mutate_all(~replace(., is.na(.), 0))
# mutate_all(funs(replace_na(.,0))) #%>% 
#   dplyr::mutate(Min_Surveys = round(Sample_Size*0.85,0)#,
#                   #Min_Remaining =  case_when(is.na(Aceptado) ~ Min_Surveys,TRUE ~ (Aceptado - Min_Surveys) * -1)
#                 )


```
```{r, include=FALSE}
########################################################################################
# Entrevistador productivity

Entrevistador_productivity <- dat %>% 
  dplyr::filter(estado == "finalizada__mobinet_") %>% 
  dplyr::group_by(Fecha = date_assessment, Entrevistador = entrevistador) %>% 
  dplyr::summarise(Encuestas = n())

# Entrevistador_productivity_many <- Entrevistador_productivity %>% 
#   dplyr::filter(Interviews > max_interv)
# 
# Entrevistador_productivity_less <- Entrevistador_productivity %>% 
#   dplyr::filter(Interviews < 3)
# 
# Entrevistador_productivity_final <- rbind(Entrevistador_productivity_many, Entrevistador_productivity_less)%>% 
#   dplyr::select(Entrevistador, Interviews) %>% 
#   arrange(desc(Entrevistador))

enum_productivity <- dat %>% 
  dplyr::filter(estado == "finalizada__mobinet_") %>% 
  group_by(Entrevistador = entrevistador) %>% 
  dplyr::summarise(Encuestas = n()) %>% 
  arrange(desc(Encuestas))


# Entrevistador per survey status 

enumer_per_survey_status <- dat %>% 
  dplyr::filter(estado == "finalizada__mobinet_") %>% 
  dplyr::group_by(Fecha = date_assessment, Entrevistador = entrevistador) %>% 
  dplyr::summarise(Aceptado = sum(time_validity != "Flagged", na.rm = T),
            Marcada_Tiempo = sum(time_validity == "Flagged", na.rm = T )
  )
enumer_per_survey_status


###############
# tracking nutritional data
antro_total <- dat %>% 
  dplyr::summarise(Cargado_Total = n(),
                   Mayores_65 = sum(presencia_65 == "si", na.rm = T),
                   Ninos_0_59 = sum(presencia_0_59_meses == "si", na.rm = T),
                   Gestantes = sum(presencia_embarazo == "si", na.rm = T)) 
antro_total <- as.data.frame(t(antro_total))
antro_total <- tibble::rownames_to_column(antro_total, "Grupo")
names(antro_total)[names(antro_total) == 'V1'] <- "Total_actual"


#popgroup_registro <- dat %>% select(registro, pop_group)
#gaggi <- merge(popgroup_registro, n_dat, by.y = "registro", all.y = T)


antro_submitted <- n_dat %>% 
  dplyr::summarise(Cargado_Total = n(),
                   Mayores_65 = sum(presencia_mayores65 == 1, na.rm = T),
                   Ninos_0_59 = sum(presencia_ninos_0_59 == 1, na.rm = T),
                   Gestantes = sum(presencia_gestantes == 1, na.rm = T)) 
antro_submitted <- as.data.frame(t(antro_submitted))

antro_submitted <- tibble::rownames_to_column(antro_submitted, "Grupo")
names(antro_submitted)[names(antro_submitted) == 'V1'] <- "Cargado"


summary_antropometric <- left_join(antro_total, antro_submitted)


summary_antropometric$Porc_Cargado <- paste0(round(100*(summary_antropometric$Cargado /
                                                    summary_antropometric$Total_actual),0),"%")


#antropometric data by population group
registro_hh <- dplyr::select(dat, registro, pop_group)
n_dat <- merge(registro_hh, n_dat, by="registro", all.y = T)

antro_by_popgroup <- n_dat %>% group_by(pop_group) %>% 
  dplyr::summarise(Cargado_Total = n(),
                   Mayores_65 = sum(presencia_mayores65 == 1, na.rm = T),
                   Ninos_0_59 = sum(presencia_ninos_0_59 == 1, na.rm = T),
                   Gestantes = sum(presencia_gestantes == 1, na.rm = T)) 



# percentage uploaded antropometric data by population group
porc_antro_by_popgroup <- n_dat %>% group_by(pop_group) %>% 
  dplyr::summarise(Cargado_Total = n(),
                   Mayores_65 = sum(presencia_mayores65 == 1, na.rm = T),
                   Ninos_0_59 = sum(presencia_ninos_0_59 == 1, na.rm = T),
                   Gestantes = sum(presencia_gestantes == 1, na.rm = T)) 
names(porc_antro_by_popgroup)
colnames(porc_antro_by_popgroup) <- c("pop_group", "Cargado_Total_recogido", "Mayores_65_recogido", "Ninos_0_59_recogido", "Gestantes_recogido")



porc_antro_total_pop <- dat %>% group_by(pop_group) %>% 
  dplyr::summarise(Cargado_Total = n(),
                   Mayores_65 = sum(presencia_65 == "si", na.rm = T),
                   Ninos_0_59 = sum(presencia_0_59_meses == "si", na.rm = T),
                   Gestantes = sum(presencia_embarazo == "si", na.rm = T)) 
names(porc_antro_total_pop)
colnames(porc_antro_total_pop) <- c("pop_group", "Cargado_Total_muestra", "Mayores_65_muestra", "Ninos_0_59_muestra", "Gestantes_muestra")



porc_summary_antropometric <- left_join(porc_antro_total_pop, porc_antro_by_popgroup, by = "pop_group")


porc_summary_antropometric$Cargado_Total <- paste0(round(100*(porc_summary_antropometric$Cargado_Total_recogido /
                                                                porc_summary_antropometric$Cargado_Total_muestra),0),"%")

porc_summary_antropometric$Mayores_65 <- paste0(round(100*(porc_summary_antropometric$Mayores_65_recogido /
                                                        porc_summary_antropometric$Mayores_65_muestra),0),"%")

porc_summary_antropometric$Ninos_0_59 <- paste0(round(100*(porc_summary_antropometric$Ninos_0_59_recogido /
                                                             porc_summary_antropometric$Ninos_0_59_muestra),0),"%")

porc_summary_antropometric$Gestantes <- paste0(round(100*(porc_summary_antropometric$Gestantes_recogido /
                                                       porc_summary_antropometric$Gestantes_muestra),0),"%")


porc_summary_antropometric$Mayores_65_957 <- paste0(round(100*(porc_summary_antropometric$Mayores_65_recogido /
                                                            196),0),"%")
porc_summary_antropometric$Ninos_0_59_957 <- paste0(round(100*(porc_summary_antropometric$Ninos_0_59_recogido /
                                                            196),0),"%")
porc_summary_antropometric$Gestantes_957 <- paste0(round(100*(porc_summary_antropometric$Gestantes_recogido /
                                                            196),0),"%")

porc_summary_antropometric <- porc_summary_antropometric[,c("pop_group", "Cargado_Total", "Mayores_65", "Ninos_0_59", "Gestantes", 
                                                  "Mayores_65_957", "Ninos_0_59_957", "Gestantes_957")]




# Survey status per day 
survey_status_per_day <- dat %>% 
  dplyr::filter(estado == "finalizada__mobinet_") %>% 
  group_by(Fecha = date_assessment) %>% 
  dplyr::summarise(Aceptado = sum(time_validity != "Delete", na.rm = T),
            Marcada_Tiempo = sum(time_validity == "Flagged" | time_validity == "Delete", na.rm = T )
  )

func <- function(z) if (is.numeric(z)) sum(z, na.rm = T) else ''
sumrow_total <- as.data.frame(lapply(survey_status_per_day, func))
sumrow_total
survey_status_per_day <- rbind(survey_status_per_day, sumrow_total ) %>% 
  mutate_all(~replace(., is.na(.), 0))

survey_status_per_day

# survey_len <- dat %>% 
#   filter(consent == "yes" & Entrevistador_num == "556") %>% 
#   dplyr::select(audit_duration)
# survey length by Entrevistador
survey_length <- dat %>% 
  dplyr::filter(estado == "finalizada__mobinet_") %>% 
  dplyr::group_by(Entrevistador = entrevistador) %>% 
  dplyr::summarise(
    Duracion_Media = round(median(as.numeric(duracion_min), na.rm = T),0)
  )%>% 
  dplyr::arrange(desc(Duracion_Media) )

overall_survey_median <- round(median(as.numeric(dat$duracion_min), na.rm = T),0)

survey_length$Mediana_Global <-  overall_survey_median



# median interview duration by day
duration_by_day <- dat%>%
  group_by(date_assessment)%>% 
  summarise(Mean=mean(duracion_min), Max=max(duracion_min), Min=min(duracion_min), Median=median(duracion_min), Std=sd(duracion_min))




# Entrevistador with short interv duration
short_interviews_by_enum <- dat %>% 
  dplyr::filter(estado == "finalizada__mobinet_") %>% 
  dplyr::filter(duracion_min < flag_time_limit) %>% 
  
  dplyr::select(Fecha = date_assessment, 
                Entrevistador = entrevistador, 
                Departamento = departamento,
                Duracion =  duracion_min,
                Grupo_Poblacion = pop_group
  ) %>% mutate(
    Duracion = round(as.numeric(Duracion),0),
  ) %>% 
  arrange(desc(Fecha) )
short_interviews_by_enum <- short_interviews_by_enum


# merge shape file with final output
df_list <- list(acogida_tracking_merged, 
                permanencia_tracking_merged, retornados_tracking_merged,
                transito_tracking_merged, pendularios_tracking_merged)

# merge all data frames in list
library(data.table)
overall_merged <- rbindlist(list(acogida_tracking_merged, 
               permanencia_tracking_merged, retornados_tracking_merged,
               transito_tracking_merged, pendularios_tracking_merged), fill = TRUE)[,lapply(.SD, sum, na.rm = TRUE) , departamento]
# join shapes with tracking table
df.map <- left_join(adm, overall_merged, by="departamento") %>%
  mutate(pct.done=pmin(Aceptado/Tamano_Muestra*100, 100))


# merge all enumerator related indicators into one table
# number of inconsistencies by enumerator
cleaning_log <- read.csv("Input/cleaning_log.csv",
               stringsAsFactors = TRUE)
incoherences <- data.frame(table(cleaning_log$entrevistador))
names(incoherences) <- c("entrevistador", "nr_inhoherencias")

# median interview duration by enumerator
duration_enumerator <- dat%>%
  group_by(entrevistador)%>% 
  summarise(duracion_mediana=median(duracion_min))

# number of flagged surveys per enumerator
dat$time_flagged <- ifelse(dat$time_validity == "Flagged",1,NA)
flagged_surveys_enumerator <- data.frame(table(dat$time_flagged, dat$entrevistador))
flagged_surveys_enumerator[,1] <- NULL
names(flagged_surveys_enumerator) <- c("entrevistador", "nr_marcada_tiempo")

full_entrevistador <- left_join(incoherences, duration_enumerator, by='entrevistador') %>%
                left_join(., flagged_surveys_enumerator, by='entrevistador', all.x = T) 
full_entrevistador <- full_entrevistador[order(full_entrevistador$nr_marcada_tiempo),]


```



<center> **Informe de Seguimiento de la Recolección de Datos** </center>


# {.tabset}
***
## Mapa

<center>**Porcentaje de encuestas completadas (todos los grupos de población combinados) por departamento** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis', fig.width=9, fig.height=7}
## Interviews Tracking (Map)
# generate map
pal.strata <- colorNumeric(c("red", "yellow", "green"), 0:100)

labels <- paste(
  "<strong>", df.map$departamento,
  "</strong><br>% Completado:", round(df.map$pct.done,  1),
  "</strong><br># Restante:", df.map$Restante, 
  "</strong><br># Marcada Tiempo:", df.map$Marcada_Tiempo) %>%
  lapply(htmltools::HTML)

leaflet(options = leafletOptions(zoomControl = FALSE,
                                 minZoom = 5.7, maxZoom = 5.7, dragging = FALSE, width = "100%")) %>%
  addPolygons(data=df.map, color = "black", weight = 0.5, opacity = 1, fill = F, fillOpacity = 0, 
              smoothFactor = 0, stroke = TRUE) %>%
  addPolygons(data=df.map, color = ~pal.strata(df.map$pct.done),
              weight = 1, opacity = 0.5, fill = T, fillOpacity = 0.7,
              label=labels) %>%
  addTiles() %>%
  addMeasure(primaryLengthUnit = "kilometers") %>% 
  addProviderTiles("Esri.WorldGrayCanvas")

```

## Controles Encuestador

<center>**Número de encuestas con incoherencias, número de encuestas inferiores a `r flag_time_limit` minutos y duración media de la entrevista por encuestador** </center> </br>

</center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}

DT::datatable(full_entrevistador,
              options = list(
                  pageLength = 2000,
                  dom = 'ft'
                )
  ) %>% 
  DT::formatStyle('nr_marcada_tiempo', fontWeight = 'bold')

```



## Progreso Recolección

<center>**Número de encuestas por Dia** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(survey_status_per_day)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```


<center>**Encuestas Completadas**</center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}

kable(interview_method_wide)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```



<center>**Medidas Antropométricas**</center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}

DT::datatable(porc_summary_antropometric,
              options = list(
                  pageLength = 2000,
                  dom = 'ft'
                )
  ) %>% 
  DT::formatStyle('Mayores_65_957',  color = 'red', fontWeight = 'bold', 'text-align' = 'center')  %>% 
  DT::formatStyle('Ninos_0_59_957',  color = 'red', fontWeight = 'bold', 'text-align' = 'center')  %>%
  DT::formatStyle('Gestantes_957',  color = 'red', fontWeight = 'bold', 'text-align' = 'center')


kable(antro_by_popgroup)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)


```



***

## Duración Encuestas
<center>**Encuestas recogidas en menos de `r flag_time_limit` minutos - últimos 7 días** </center> </br>
  

```{r eval=TRUE, echo=FALSE, results='asis'}

DT::datatable(short_interviews_by_enum,
              options = list(
                  pageLength = 2000,
                  dom = 'ft'
                )
  ) %>% 
  DT::formatStyle('Duracion',  color = 'red', fontWeight = 'bold') %>% 
  DT::formatStyle('Entrevistador',  color = 'black', fontWeight = 'bold')

```
***
***


 <center>**Mediana de la duración de la Entrevista por Encuestador** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(survey_length)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```

***
***

 <center>**Mediana de la duración de la Entrevista por dia** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(duration_by_day)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```



##  Productividad Encuestadores

<center>**Encuestadores con una Productividad Baja o Alta** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}
kable(enum_productivity)%>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"),fixed_thead = T, full_width = F)
```


## Progreso Encuestadores

<center>**Número de Encuestas por Día por Encuestador** </center> </br>

```{r eval=TRUE, echo=FALSE, results='asis'}

DT::datatable(enumer_per_survey_status,
              options = list(
                  pageLength = 2000,
                  dom = 'ft'
                )
  ) %>% 
  DT::formatStyle('Marcada_Tiempo',  color = 'red', fontWeight = 'bold') %>% 
  DT::formatStyle('Aceptado',  color = 'green', fontWeight = 'bold')

```


## Comunidad de Acogida

```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(acogida_tracking_merged,
              options = list(
                  pageLength = 130,
                  dom = 'ft'
                )
              ) %>% 
  DT::formatStyle('Borrado',  color = 'red', fontWeight = 'bold') %>% 
  DT::formatStyle('Aceptado',  color = 'green', fontWeight = 'bold') %>% 
  DT::formatStyle('Marcada_Tiempo',  color = 'red', fontWeight = 'bold') %>%
  #DT::formatStyle('Min_Remaining',  color = 'blue', fontWeight = 'bold') %>% 
  DT::formatStyle('Restante', fontWeight = 'bold')
```


## Migrantes Vocación de Permanencia

```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(permanencia_tracking_merged,
              options = list(
                  pageLength = 130,
                  dom = 'ft'
                )
              ) %>% 
  DT::formatStyle('Borrado',  color = 'red', fontWeight = 'bold') %>% 
  DT::formatStyle('Aceptado',  color = 'green', fontWeight = 'bold') %>% 
  DT::formatStyle('Marcada_Tiempo',  color = 'red', fontWeight = 'bold') %>%
  #DT::formatStyle('Min_Remaining',  color = 'blue', fontWeight = 'bold') %>% 
  DT::formatStyle('Restante', fontWeight = 'bold')
```



## Retornados Colombianos

```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(retornados_tracking_merged,
              options = list(
                  pageLength = 130,
                  dom = 'ft'
                )
              ) %>% 
  DT::formatStyle('Borrado',  color = 'red', fontWeight = 'bold') %>% 
  DT::formatStyle('Aceptado',  color = 'green', fontWeight = 'bold') %>% 
  DT::formatStyle('Marcada_Tiempo',  color = 'red', fontWeight = 'bold') %>%
  DT::formatStyle('Restante', fontWeight = 'bold')
```


## Pendularios

```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(pendularios_tracking_merged,
              options = list(
                  pageLength = 130,
                  dom = 'ft'
                )
              ) %>% 
  DT::formatStyle('Borrado',  color = 'red', fontWeight = 'bold') %>% 
  DT::formatStyle('Aceptado',  color = 'green', fontWeight = 'bold') %>% 
  DT::formatStyle('Marcada_Tiempo',  color = 'red', fontWeight = 'bold') %>%
  DT::formatStyle('Restante', fontWeight = 'bold')
```


## Migrantes Transito

```{r eval=TRUE, echo=FALSE, results='asis'}
DT::datatable(transito_tracking_merged,
              options = list(
                  pageLength = 130,
                  dom = 'ft'
                )
              ) %>% 
  DT::formatStyle('Borrado',  color = 'red', fontWeight = 'bold') %>% 
  DT::formatStyle('Aceptado',  color = 'green', fontWeight = 'bold') %>% 
  DT::formatStyle('Marcada_Tiempo',  color = 'red', fontWeight = 'bold') %>%
  DT::formatStyle('Restante', fontWeight = 'bold')
```
